### 2020-10-08 conclusion.tex
some conclusions

\paragraph{Conclusion}
In this paper...
\end{document}

>>>>

\paragraph{Conclusion and Future Work}
In this paper we presented Priority GV, which is a functional language with session types. We used priorities in session types, following Priority CP \cite{dardha2018} to guarantee deadlock freedom statically via our priority-based type system. We proved the progress property of PGV in \Cref{lem:pgv-closed-progress-confs}. We also presented an updated version of PCP, where we moved from commuting conversions to structural congruence in the reduction relation, thus remaining faithful to the reduction relation of the $\pi$-calculus. Finally, we presented an encoding of Priority CP to Pririty GV in \Cref{fig:pcp-to-pgv}. For this translation we proved that it is sound with respect to typing (\Cref{{lem:pcp-to-pgv-terms-preservation}}, \Cref{thm:pcp-to-pgv-confs-preservation}) and operational semantics, given by operational correspondence soundness (\Cref{thm:pcp-to-pgv-operational-correspondence-soundness}) and completeness (\Cref{thm:pcp-to-pgv-operational-correspondence-completeness}).

As future work we intend to define the inverse encoding from Priority GV to Priority CP...
\end{document}
